### 2008-09-29 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

\textbf{Def 1-} \emph{Set of Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}. We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\

@@

\textbf{Def 7-} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

\textbf{Def 8-} \emph{Correctness}: A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program. Behavior for an operation means the data it has read. Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence.\\

@@

\section{Rules For }

>>>>

textbf{Def 1-} \emph{Set of Primitive Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}. We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\

@@

\textbf{Def 7-} \emph{Precedence Relationship For Transactions:} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

\textbf{Def 8-} \emph{Correctness:} A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program. Behavior for an operation means the data it has read or wants to write. Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence. However writs always writes the same value no matter what. Hence the behavior of a write operation is not alterable

@@

\subsection{Rules}
